Timeliness of security updates for Android

### 2014-08-27 securityupdates.tex
Fix jelly bean citation

\section{Discussion}
There are continuing efforts to reduce the impact of root vulnerabilities, both in Android and more widely.
SEAndroid~\cite{Smalley2013} which is included in Android from version 4.1~\cite{https://developer.android.com/about/versions/jelly-bean.html} claimed to prevent some root vulnerabilities and to reduce the impact of others.
Capability based enforcement systems such as Capsicum~\cite{Watson2010} substantially reduce the capabilities that an exploit has to try and gain increased privilege with.
When Capsicum is included in Linux~\cite{TODO} and hence in Android, it could be used to place fine grained restrictions on system daemons, preventing vulnerabilities becoming root vulnerabilities.

>>>>

\section{Discussion}
There are continuing efforts to reduce the impact of root vulnerabilities, both in Android and more widely.
SEAndroid~\cite{Smalley2013} which is included in Android from version 4.1~\cite{jelly-bean-release} claimed to prevent some root vulnerabilities and to reduce the impact of others.
Capability based enforcement systems such as Capsicum~\cite{Watson2010} substantially reduce the capabilities that an exploit has to try and gain increased privilege with.
When Capsicum is included in Linux~\cite{TODO} and hence in Android, it could be used to place fine grained restrictions on system daemons, preventing vulnerabilities becoming root vulnerabilities.
